Growth model analysis 3spp WB

### 2018-12-14 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added relImpOccAll_GR_HorizBarsColor graph

  # make bar chart of relative importance of each variable for each spp
  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
               ageGroup = ageGroupLoop,
               season = seasonLoop)

@@

ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
  geom_col() +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-1.0, -0.5, 0.0, 0.5),
                     labels = c('1.0', '0.5', '0.0', '0.5')) +
  theme_publication() +
  scale_fill_grey(start = 0.15, end = 0.75) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))

@@

>>>>

  # make bar chart of relative importance of each variable for each spp
  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
               ageGroup = ageGroupLoop,
               season = seasonLoop
               )
  rI$varText <- rep(names(relImpAll[['bkt']]$lmg),2)

@@

### get prop env
summ1 <- rIAll %>%
  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
  group_by(rowname,isEnvVar,ageGroup, season) %>%
  summarize(mean=mean(value)) %>%
  arrange(ageGroup,season,rowname,isEnvVar)

summ2 <- summ1 %>%
  group_by(rowname,ageGroup,season) %>%
  summarize(sum=sum(mean))

summ1a <- left_join(summ1,summ2) %>%
  mutate(prop = mean/sum,
         xAxisLoc = ifelse(rowname == 'bktRI',-0.85, 0.85)) %>%
  filter(isEnvVar == 1) 
###

####
# add in betas to rIAllMinus
load("D:/projects/linkedModels/data/out/allBetas.RData") #loads df 'q'
qFig1 <- q %>% filter(riverGG == 'WB', species %in% c('bkt','bnt'))
qFig1$season <- as.numeric(as.character(qFig1$season))
qFig1$isYOY <- as.numeric(as.character(qFig1$isYOY))
qFig <- qFig1 %>%
  mutate( varText = tolower(betaGG)) %>%
  mutate( varText = ifelse(varText == 'temp*flow','temp:flow', varText)) %>%
  mutate( varText = ifelse(varText == 'bnt*bkt','bkt:bnt', varText)) %>%
  select(isYOY,season,species,median,varText)

# prepare rIAllMinus
rIAllMinusQ <- rIAllMinus %>%
  mutate(species = str_sub(rowname,1,3),
         isYOY = ageGroup) %>%
  left_join(qFig) %>%
  mutate(median01 = ifelse(median > 0, 1, 0),
         medianBreaks = cut(median, breaks = c(-1, -0.025, 0 , 0.025, 1)))

#

ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
  geom_col() +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-1.0, -0.5, 0.0, 0.5),
                     labels = c('1.0', '0.5', '0.0', '0.5')) +
  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2)), color=rowname),size = 5) +
  scale_color_grey(start = 0.15, end = 0.75) +
  theme_publication() +
  scale_fill_grey(start = 0.15, end = 0.75) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))

@@

ggplot(rIAllMinusQ, aes(var, y = value2)) +
  geom_col(aes(fill = median)) +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-0.9, -0.25, -0.5, 0.0, 0.25, 0.5, 0.9),
                     labels = c('0.9', '0.25', '0.5\n\nBrook Trout\n', '0.0', '0.25', '0.5\n\nBrown Trout\n', '0.9')) +
  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2))),size = 5) +
  geom_hline(yintercept = 0) +
  #scale_color_grey(start = 0.15, end = 0.75) +
  theme_publication() +
 #  scale_fill_continuous() +
  scale_fill_distiller(name="Parameter\nestimate", palette = "RdBu", direction = 1) +
  theme(legend.position="right",             
        #legend.key = element_rect(colour = NA),
        legend.direction = "vertical",
        legend.key.size= unit(0.25, "in"),
        #    legend.margin = unit(0, "cm"),
        legend.title = element_text(face="plain")#element_blank()
        ) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))

ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBarsColor.png'), width = 11, height = 9, units='in')
